Title here

### 2020-07-16 analysis/paper/paper.tex
some results

\subsubsection{Definition of indexes}

@@

To separate between the zonally symmetric and asymmetric components of
the SAM, we computed the zonal mean and anomalies of the full SAM
spatial pattern. The results are shown in Figure~\ref{fig:method} for
700hPa. The full spatial signal (\(\mathrm{EOF_1}(\lambda, \phi)\)) is
the sum of the zonally asymmetric (\(\mathrm{EOF_1^*}(\lambda, \phi)\))
and symmetric (\([\mathrm{EOF_1}](\lambda, \phi)\)) components. We then
compute the ``Full'', ``Asymmetric'' and ``Symmetric'' indexes, by
regressing each geopotential field on these patterns (weighting by the
cosine of latitude).

The three indexes are normalised by dividing them by the standard
deviation of the ``Full'' index at each level. This means that comparing
the magnitude between indexes is meaningful, but it also means that not
every index will have unit standard deviation.

@@

@@

@@

Sem tortor mus non tristique augue. Donec vel feugiat sit aliquet lorem
dui lobortis dolor risus. Proin, ac eu, mauris. Dolor id habitasse,
curabitur platea ante. Rhoncus volutpat himenaeos vestibulum ut bibendum
felis non. Ligula placerat ac luctus ad. Ante, lorem volutpat eu dapibus
pharetra arcu. Sollicitudin eu tortor amet. Maecenas nulla euismod ac
suspendisse metus. A ac, hendrerit, sit sollicitudin ac primis
ullamcorper tempor id, mauris. Sem diam, sem curabitur. Risus, nullam
vel diam hendrerit massa nec non. Donec amet amet ultrices ac taciti
aliquam. Enim arcu et sed sit.

Ligula sed sociosqu imperdiet magna curabitur, et, elit lobortis ut,
sed. Placerat id eros quis vivamus sed, in felis. Egestas phasellus at
sagittis sed senectus malesuada. Vestibulum at pretium elementum id,
facilisi. Porttitor luctus vel tempus diam nec per, nibh nisi. Viverra
turpis nisl sed nec varius, et ridiculus in amet. Amet sapien nec
convallis arcu dis et mauris dolor. Vestibulum, in, in tincidunt tellus
risus class quisque, augue feugiat.

@@

\begin{figure}
\includegraphics{A2-1} \appendcaption{A2}{Fourier spectrum of each timeseries. The shading indicates de 95\% qunatile derived fitting an AR process and bootstrapping 5000 simulated samples.}\label{fig:A2}
\end{figure}

@@

>>>>

\subsubsection{Definition of indices}

@@

To separate between the zonally symmetric and asymmetric components of
the SAM, we computed the zonal mean and anomalies of the full SAM
spatial pattern. The results are shown in Figure~\ref{fig:method} for
700hPa. The full spatial signal (\(\mathrm{EOF_1}(\lambda, \phi)\)) is
the sum of the zonally asymmetric (\(\mathrm{EOF_1^*}(\lambda, \phi)\))
and symmetric (\([\mathrm{EOF_1}](\lambda, \phi)\)) components. We then
compute the ``Full'', ``Asymmetric'' and ``Symmetric'' indices, by
regressing each geopotential field on these patterns (weighting by the
cosine of latitude).

The three indices are normalised by dividing them by the standard
deviation of the ``Full'' index at each level. This means that comparing
the magnitude between indices is meaningful, but it also means that not
every index will have unit standard deviation.

@@

Figure\textasciitilde{}\ref{fig:asymsam-timeseries} shows the resulting
Asymmetric and Symmetric time series corresponding to 700 and 30hPa.
blablababla

\begin{itemize}
\item
  stratosphere clearly nor normally distributed. a lot of values near 0
  and some relatively high outliers. Especially true int he case of the
  asymmetric index. High frequency variablity.
\item
  In both levels, there's correlation between the series (expected),
\end{itemize}

Correlations between the Asymmetric and Symmetric series are rather
constant throught the troposphere, fluctiating between 0.39 and 0.45
(Figure\textasciitilde{}\ref{fig:cor-lev}). Futhermore, the
cross-correlation of each series across levels --shown in
Figure\textasciitilde{}\ref{fig:cross-correlation}-- are high in the
trosposphere (greater than 0.9) for both indices. This suggests that
both the Asymmetric and the Symemtric component of the tropospheric SAM
are highly vertically coherent, both in their individual evolution and
their temporal relationship. This is to be expected since the SAM is
mostly equivalent barotropic (citaaaa).

In the stratosphere the situation is different. As can be seen in
Figure\textasciitilde{}\ref{fig:cor-lev}, the relationship between the
Asymmetric and Symmetric indices varies with height above 100 hPa. It
starts to decreese right over the tropopause, reaches a minium of 0.21
at 20 hPa and then it increases again monotonically with height up to
the uppermost level of the reanalysis. The cross-correlation across
levels in the stratosphere is generally weaker than in the troposphere
(Figure\textasciitilde{}\ref{fig:cross-correlation}). Furthermore, above
100 hPa, the cross-correlation decreases more rapdily with height for
the Symmetric SAM than for the Asymmetric SAM as evidenced by the wider
dark red areas near the diagonal in
Figure\textasciitilde{}\ref{fig:cross-correlation}b)
vs.~Figure\textasciitilde{}\ref{fig:cross-correlation}c). Moreover, the
stratospheric Symmetric SAM seems to be slightly more connected to the
trosposphere than the Asymmetric SAM; this can be seen by the lower
correlation values in the top right quadrant of
Figure\textasciitilde{}\ref{fig:cross-correlation}b) in comparison with
Figure\textasciitilde{}\ref{fig:cross-correlation}c).

@@

Figure\textasciitilde{}\ref{fig:cross-correlation}a) show the
cross-correlation across levels for the Full SAM index. \ldots{}..

To undertand the spatial patterns associated with both indeces we
regressed monthly geopotential anomalies into both indeces using
multiple regression (Figure A6 illustrates the difference between
computing two simple regressions and one multiple regression).

@@

Figure\textasciitilde{}\ref{fig:2d-regr} shows the spatial year-long
regression for selected levels. In the troposphere the Full annular mode
is clearly ``contaminated'' with well known zonal asymemtries (panels g
and j) which are succesfully sepparated by our methodology (panels h, i,
k and l). In the stratosphere, the spatial pattern associated with the
Full SAM is much more clearly dominated by a zonally symmetric,
monopolar structure (panels a and d) that is, however, not perfectly
centered in the south pole. The monopoloe obtained by multiple
regression with the Asymmetric and Symmetric SAM (panels c and f in
Figure\textasciitilde{}\ref{fig:2d-regr}) is much more symmetric and the
shift from total symmetry is captured by the regression pattern of the
Asymmetric SAM as a wave-1 pattern (panels b and e).

\begin{figure}
\includegraphics{vertical-regression-1} \caption[Asymmetric coefficient of the multiple regression of mean monthly geopotential height anomalies between 65 and 40 South]{Asymmetric coefficient of the multiple regression of mean monthly geopotential height anomalies between 65 and 40 South. Values are standarised by the standard deviation at each level. (this caption needs some love)}\label{fig:vertical-regression}
\end{figure}

@@

\begin{figure}
\includegraphics{ccf-levels-1} \caption[Cross-correlation functions for each index and two differnet base levels]{Cross-correlation functions for each index and two differnet base levels.}\label{fig:ccf-levels}
\end{figure}

\begin{figure}
\includegraphics{A2-1} \appendcaption{A2}{Fourier spectrum of each timeseries. The shading indicates de 95\% area derived by fitting an AR process to each series and bootstrapping 5000 simulated samples.}\label{fig:A2}
\end{figure}

@@

\begin{figure}
\includegraphics{A5-1} \appendcaption{A5}{Regression pattern of precipiation with Asymmetric and Symmetric SAM. P-values smaller than 0.05 (controlling for Flase Detection Rate) as hatched areas.}\label{fig:A5}
\end{figure}

\begin{figure}
\includegraphics{A6-1} \appendcaption{A6}{Regressions maps resulting from performing one multiple regression (a. and b.) and from performing two simple regressions (c. and d.)}\label{fig:A6}
\end{figure}
